### 2019-01-29 micro3_3.tex
Micro

There can be two approaches, namely:
A feasible allocation $(z_1^*, z_2^*)$ is efficient $\iff\ \exists\ \bar{f} \ge 0$ such that $(z_1^*, z_2^*)$ solves the following optimization problem 
\begin{align*}
\underset{z_{11} z_{21} \ge 0}{\max}\ f_1(z_{11}, z_{21})\\
s.t.\ f_2(z_{12}, z_{22}) \ge \bar{f}\\
z_{11} + z_{12} = \bar{z_1}\\
z_{21} + z_{22} = \bar{z_2}
\end{align*}
or:
A feasible allocation $(z_1^*, z_2^*)$ is efficient $\iff\ \exists\ \lambda_1 \ge 0, \lambda_2 \ge 0: \lambda_1^2 + \lambda_2^2 > 0$ such that $(z_1^*, z_2^*)$ solves the following optimization problem:
\begin{align*}
\underset{z_{11}, z_{21}, z_{12}, z_{22} \ge 0}{\max}\ \lambda f_1(z_{11}, z_{21}) + (1 - \lambda)f_2(z_{12}, z_{22})\\
s.t. z_{11} + z_{12} = \bar{z_1}\\
	z_{12} + z_{22} = \bar{z_2}
\end{align*}
\section*{Problem 4}
Assuming interior solutions, show that the first order conditions of problems (16.E.1)
and (16.F.1) in the textbook are equivalent to each other. Under what conditions on utility
functions will the two problems lead to the same solutions? Explain your answer.

@@

@@

If utility functions are concave then the utility possibility set is a convex set. Obviously for each particular $(\bar{u_2}, \dots, \bar{U_I})$ the solution to the problem 16.F.1. should lie on the frontier (see Fig.), but when the UPS is a convex set by the separating hyperplane theorem there should exists such a non-zero $\lambda = (\lambda_1\ \dots\ \lambda_I)$ such that is is a solution to the problem 16.E.1.
	\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\textwidth]{plotdraft}
	\caption{}\label{fig2}
\end{figure}
In that sense both problems will lead to the same solution.
\section*{Problem 5}
Consider the exchange economy depicted in Figure 15.B.10(a). Show that the initial
endowment allocation can be supported as a part of a quasi-equilibrium with transfers.
Describe the corresponding price vector and wealth distribution. Is this a full equilibrium
with transfers?

>>>>

There can be two approaches, namely:
A feasible allocation $(z_1^*, z_2^*)$ is efficient $\iff\ \exists\ \bar{f} \ge 0$ such that $(z_1^*, z_2^*)$ solves the following optimization problem 
\begin{align*}
\underset{z_{11} z_{21} \ge 0}{\max}\ f_1(z_{11}, z_{21})\\
s.t.\ f_2(z_{12}, z_{22}) \ge \bar{f}\\
z_{11} + z_{12} = \bar{z_1}\\
z_{21} + z_{22} = \bar{z_2}
\end{align*}
or:
A feasible allocation $(z_1^*, z_2^*)$ is efficient $\iff\ \exists\ \lambda_1 \ge 0, \lambda_2 \ge 0: \lambda_1^2 + \lambda_2^2 > 0$ such that $(z_1^*, z_2^*)$ solves the following optimization problem:
\begin{align*}
\underset{z_{11}, z_{21}, z_{12}, z_{22} \ge 0}{\max}\ \lambda_1 f_1(z_{11}, z_{21}) + \lambda_2f_2(z_{12}, z_{22})\\
s.t. z_{11} + z_{12} = \bar{z_1}\\
	z_{12} + z_{22} = \bar{z_2}
\end{align*}
\section*{Problem 4}
Assuming interior solutions, show that the first order conditions of problems (16.E.1)
and (16.F.1) in the textbook are equivalent to each other. Under what conditions on utility
functions will the two problems lead to the same solutions? Explain your answer.

@@

In both problems technological constraints are the same hence FOCs wrt $y_j$ will be similar in both problems either.

@@

If utility functions are concave then the utility possibility set is a convex set. Obviously for each particular $(\bar{u_2}, \dots, \bar{u_I})$ the solution to the problem 16.F.1. should lie on the frontier (see Fig. \ref{fig2}), but when the UPS is a convex set by the separating hyperplane theorem there should exists such a non-zero $\lambda = (\lambda_1\ \dots\ \lambda_I)$ such that it is a solution to the problem 16.E.1.
	\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\textwidth]{plotdraft}
	\caption{}\label{fig2}
\end{figure}
In that sense both problems will lead to the same solution. Put it another way, both problems have identical FOCs, but only under assumption of concavity these FOCs become \textit{sufficient} conditions for extremum.
\section*{Problem 5}
Consider the exchange economy depicted in Figure 15.B.10(a). Show that the initial
endowment allocation can be supported as a part of a quasi-equilibrium with transfers.
Describe the corresponding price vector and wealth distribution. Is this a full equilibrium
with transfers?
